European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-25 manuscript/manuscript.qmd
Move economic indicators to covariate section

\color{red}
However, empirical studies suggested that countries with low international reserves, high current account deficits, and low GDP growth are more likely to receive IMF funding assistance [@barro2005; @knight1997], despite such indicators often reflecting a limited capacity to repay.
\color{black}

@@

We also include economic performance indicators such as GDP, per capita GDP, and lagged GDP growth as determinants of lending and borrowing behaviour. International reserves as a share of imports are used to capture a country’s ability to finance its balance of payments without IMF support. Finally, a binary indicator for OECD membership is included to proxy for institutional and economic differences among countries.

>>>>

@@

We include a range of economic performance indicators that have been shown to systematically affect IMF lending decisions [@barro2005; @knight1997]. To capture these dynamics, we include GDP, per capita GDP, and lagged GDP growth as proxies for macroeconomic performance. International reserves as a share of imports are used to measure a country’s external liquidity and ability to manage balance-of-payments pressures without IMF support. Finally, a binary variable for OECD membership serves as a proxy for broader institutional and economic differences among countries.
